A Type System for String Sanitation\\Implemented Inside a Python

### 2014-08-05 sanitation-psp14/sanitation-psp14-short.tex
Improved description of proof a bit.

\begin{thm}
If $S : \strin{r}$ then there exists a P such that $\trden{s} = P$ and either: 
(a) $P \treduces \tstr{s}$ and $S \sreduces \strin{s}$, and $s \in lang{r}$; or
(b) $P \err$ and $S \err$.
\end{thm}

>>>>

\begin{thm}
If $S : \strin{r}$ then there exists a P such that $\trden{s} = P$ and either: 
(a) $P \treduces \tstr{s}$ and $S \sreduces \strin{s}$, and $s \in \lang{r}$; or
(b) $P \err$ and $S \err$.
\end{thm}
